Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-07-23 ms.tex
investigated the subarray size confusion some more, ruling out the 1/f smoothing method. More likely reference pixels.

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{SUBGRISM256}
\fig{azlab_ratio_tser_stripe128.pdf}{0.33\textwidth}{SUBGRISM128}
\fig{azlab_ratio_tser_stripe64.pdf}{0.33\textwidth}{SUBGRISM64}}}
{\gridline{\fig{azlab_ratio_tser_subarraySize_256.pdf}{0.33\textwidth}{SUBGRISM256}
\fig{azlab_ratio_tser_subarraySize_128.pdf}{0.33\textwidth}{SUBGRISM128}
\fig{azlab_ratio_tser_subarraySize_064.pdf}{0.33\textwidth}{SUBGRISM64}}}
\caption{The subarray size tests show very similar precision levels with a background aperture horizontally displayed from the source aperture (top row).
If no background subtraction is done, paradoxically, the tallest subgrism (fewest groups) is the most stable. \textbf{\textcolor{red}{How does this make sense? Did I possibly change how the side reference pix correction was done between the 3 tests? Changed from the FFT-based method to savgol on Fri Jul 12 22:04:54 2019. Processed the files on Jul 10 18:06. Could this be important? I will try and experiment on darks as well as re-processing the original baseline data to see.} }}\label{fig:subarraySizes}
\end{figure*}

>>>>

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{SUBGRISM256}
\fig{azlab_ratio_tser_stripe128.pdf}{0.33\textwidth}{SUBGRISM128}
\fig{azlab_ratio_tser_stripe64.pdf}{0.33\textwidth}{SUBGRISM64}}}
{\gridline{\fig{azlab_ratio_tser_subarraySize_256.pdf}{0.33\textwidth}{SUBGRISM256}
\fig{azlab_ratio_tser_subarraySize_128.pdf}{0.33\textwidth}{SUBGRISM128}
\fig{azlab_ratio_tser_subarraySize_064.pdf}{0.33\textwidth}{SUBGRISM64}}}
\caption{The subarray size tests show very similar precision levels with a background aperture horizontally displayed from the source aperture (top row).
If no background subtraction is done, paradoxically, the tallest subgrism (fewest groups) is the most stable. \textbf{\textcolor{red}{How does this make sense? Did I possibly change how the side reference pix correction was done between the 3 tests? Changed from the FFT-based method to savgol on Fri Jul 12 22:04:54 2019. 
Processed the files on Jul 10 18:06. Indeed, they were processed slightly differently, but the smoothing method matters very little.
Karl very astutely points out that the 2048x256 has reference pixels on the top but the 2048x128 and 2048x64 do NOT have reference pixels at the top, so pre-amp reset issues are very likely.} }}\label{fig:subarraySizes}
\end{figure*}
